Automatic Matching of Bullet Lands

### 2015-12-31 imaging-paper.Rnw
Small typo

library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)
library(grid)
library(gridExtra)
library(zoo)
library(tidyr)
library(rpart)
library(rpart.plot)
library(xtable)
library(sm)

>>>>

library(RColorBrewer)
library(ggplot2)
library(scales)
library(dplyr)
library(x3pr)
library(x3prplus)
library(grid)
library(gridExtra)
library(zoo)
library(tidyr)
library(rpart)
library(rpart.plot)
library(xtable)
library(sm)
@
